A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-07-12 latex-selfcontained/article.tex
some old latex changes, draw schematics post review

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{../img/approach_schematic_21pt.png}}
	\caption{A high-level overview of the proposed approach. Demonstrations are recorded with motion capture equipment, a split and cropped data set augmented with target coordinates and a gripper actuation signal is created. This is used to train neural network models in behavioral cloning. When operating in the open-loop regime, prior model outputs are used to autoregressively predict subsequent states. The resulting sequence can then be fed into a Cartesian motion planner to control a robot.}
	\label{fig:approach}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{../img/mocap_process.jpg}}
	\caption{Motion capture equipment and demonstration acquisition process. }
	\label{fig:fig1}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{../img/preprocess_pipeline_bigfont_axes.png}} 
	\caption{Pre-processing pipeline overview. All charts show effector x-axis position with respect to time.}
	\label{fig:fig2}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{../img/target_regression_waxes.jpg}}
	\caption{Estimation of the throw target coordinates. Bottle position data is used to annotate each demonstration -- consisting of effector pose observations -- with throw target coordinates. Regression on the z-axis is used to find the ground plane intersection time, at which extrapolated x- and y-coordinate values are found.}
	\label{fig:fig3}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{
		\centering
		\begin{subfigure}{0.48\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../img/vis_only.png}
			\caption{Visualization of the inferred trajectory in \emph{rviz}.}
			\label{fig:viz}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../img/exec_only.png}
			\caption{Throw execution on a \emph{Universal Robots UR5e}.}
			\label{fig:exec}
		\end{subfigure}
	}
	\caption{Qualitative performance evaluation -- visualization and execution. In both cases, the trajectories were sequences of pose (position, orientation) goals obtained by running the models autoregressively on their outputs at prior time steps. Release timing is represented in (a) by the change in marker size.}
	\label{fig:vis_exec}
\end{figure}

@@

\begin{figure}[!b]
	\centering
	\fbox{\includegraphics[width=\reswidth]{../img/modeltype_comparison.png}}
	\caption{Results -- comparison between model architectures (\emph{Naive} -- refers to the feedforward architecture, also ``naive behavioral cloning''), the best performance attained in each class. Top row metrics -- cosine similarity (dimensionless), Euclidean distance (all features, no specific unit); mean position error (stepwise,  meters). Bottom row -- mean rotation error (stepwise, radians), mean throw error (meters).}
	\label{fig:res_model_compare}
\end{figure}

\begin{figure}[!hbt]
	\centering
	\fbox{\includegraphics[width=\reswidth]{../img/each_model_best_perf.png}}
	\caption{Results -- best mean throw error performance for each hyperparameter value, in units of meters. The top row shows feedforward model results, the bottom -- RNN. In both cases, the smaller, newer dataset with less variance in orientation and target coordinates results in better throw evaluations.  Introducing the time signal significantly improves feedforward model performance, whereas for the RNN improved results could be attained at higher learning rates. In the case of the feedforward model, training for too long and making the model too large initially appears to be detrimental, while for the RNN no clear trend was observed in this respect.}
	\label{fig:rnn_naive_best}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\fbox{\includegraphics[width=16cm]{../img/ind_rnn_naive.png}}
	\caption{Results -- cosine similarity (dimensionless) and mean throw error (meters) metrics for feedforward and recurrent models, only varying in the perceptron count parameter (others held constant) -- best 2 on train and validation sets each.}
	\label{fig:ind_rnn_naive}
\end{figure}

@@

\bibliographystyle{unsrtnat}
\bibliography{references}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .

>>>>

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{img/approach_schematic_21pt.png}}
	\caption{A high-level overview of the proposed approach. Demonstrations are recorded with motion capture equipment, a split and cropped data set augmented with target coordinates and a gripper actuation signal is created. This is used to train neural network models in behavioral cloning. When operating in the open-loop regime, prior model outputs are used to autoregressively predict subsequent states. The resulting sequence can then be fed into a Cartesian motion planner to control a robot.}
	\label{fig:approach}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{img/mocap_process.jpg}}
	\caption{Motion capture equipment and demonstration acquisition process. }
	\label{fig:fig1}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{img/preprocess_pipeline_bigfont_axes.png}} 
	\caption{Pre-processing pipeline overview. All charts show effector x-axis position with respect to time.}
	\label{fig:fig2}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{img/target_regression_waxes.jpg}}
	\caption{Estimation of the throw target coordinates. Bottle position data is used to annotate each demonstration -- consisting of effector pose observations -- with throw target coordinates. Regression on the z-axis is used to find the ground plane intersection time, at which extrapolated x- and y-coordinate values are found.}
	\label{fig:fig3}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{
		\centering
		\begin{subfigure}{0.48\textwidth}
			\centering
			\includegraphics[width=\textwidth]{img/vis_only.png}
			\caption{Visualization of the inferred trajectory in \emph{rviz}.}
			\label{fig:viz}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\textwidth}
			\centering
			\includegraphics[width=\textwidth]{img/exec_only.png}
			\caption{Throw execution on a \emph{Universal Robots UR5e}.}
			\label{fig:exec}
		\end{subfigure}
	}
	\caption{Qualitative performance evaluation -- visualization and execution. In both cases, the trajectories were sequences of pose (position, orientation) goals obtained by running the models autoregressively on their outputs at prior time steps. Release timing is represented in (a) by the change in marker size.}
	\label{fig:vis_exec}
\end{figure}

@@

\begin{figure}[!b]
	\centering
	\fbox{\includegraphics[width=\reswidth]{img/modeltype_comparison.png}}
	\caption{Results -- comparison between model architectures (\emph{Naive} -- refers to the feedforward architecture, also ``naive behavioral cloning''), the best performance attained in each class. Top row metrics -- cosine similarity (dimensionless), Euclidean distance (all features, no specific unit); mean position error (stepwise,  meters). Bottom row -- mean rotation error (stepwise, radians), mean throw error (meters).}
	\label{fig:res_model_compare}
\end{figure}

\begin{figure}[!hbt]
	\centering
	\fbox{\includegraphics[width=\reswidth]{img/each_model_best_perf.png}}
	\caption{Results -- best mean throw error performance for each hyperparameter value, in units of meters. The top row shows feedforward model results, the bottom -- RNN. In both cases, the smaller, newer dataset with less variance in orientation and target coordinates results in better throw evaluations.  Introducing the time signal significantly improves feedforward model performance, whereas for the RNN improved results could be attained at higher learning rates. In the case of the feedforward model, training for too long and making the model too large initially appears to be detrimental, while for the RNN no clear trend was observed in this respect.}
	\label{fig:rnn_naive_best}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\fbox{\includegraphics[width=16cm]{img/ind_rnn_naive.png}}
	\caption{Results -- cosine similarity (dimensionless) and mean throw error (meters) metrics for feedforward and recurrent models, only varying in the perceptron count parameter (others held constant) -- best 2 on train and validation sets each.}
	\label{fig:ind_rnn_naive}
\end{figure}

@@

\bibliographystyle{unsrtnat}
\bibliography{references.bib}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .
